Wigglyhedra

### 2024-06-11 draft/wigglyhedra.tex
Some more writing.

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}[theorem]{Question}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{defprop}[theorem]{Definition/Proposition}
\crefname{notation}{Notation}{Notations}
\crefname{problem}{Problem}{Problems}

@@

Let \(P_i\) denote the indecomposable projective \(A_m\)-module defined as \(P_i = A_m\cdot e_i\).
For any integer \(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).
Let \(\mathcal{C}_m\) be the smallest triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\) (see, e.g.,~\cite[Section 2.3.3]{bap.deo.lic:22} for further discussion on the construction).

The category \(\mathcal{C}_m\) is \(k\)-linear and triangulated, where \([1]\) denotes the triangulated shift.
For \(X, Y \in \mathcal{C}_m\), let \(\Hom^{g,h}(X,Y)\) denote the space of morphisms in \(\mathcal{C}_m\) of internal degree \(g\) and homological degree \(h\).
In other words, we have
\[\Hom^{g,h}(X,Y) = \Hom(X,Y\langle g \rangle[h]).\]
Furthermore, for any integers \(a\) and \(b\), we have
\[\Hom^{g,h}(X\langle g' \rangle[h'], Y\langle g' \rangle[h']) = \Hom^{g,h}(X,Y).\]

@@

We now describe the full subcategory of \emph{linear complexes} of \(\mathcal{C}_m\).
It is convenient to think of an object \(P^{\bullet}\) of \(\mathcal{C}_m\)
as bigraded (projective) \(A_m\)-module equipped with a differential \(d \colon P^{\bullet} \to P^{\bullet}\).
More precisely, we can write
\[P^{\bullet} = \bigoplus M_i\langle g \rangle[h],\]
where \(g\) is the internal grading shift, and \(h\) is the homological grading shift, and 
each object \(M_i\) is a direct sum of copies of objects in \(\{P_1,\ldots, P_m\}\).

Recall that an object of the form \(M_i[h]\) is placed in homological degree \(-h\);
since the differential \(d\) raises the homological degree by one, it \emph{lowers} the homological shift by one.
That is, we have
\[d \colon M_i\langle g \rangle[h] \to \bigoplus M_{i'}\langle g' \rangle[h-1].\]
In other words, \(d\) maps \(P^h\) to \(P^{h-1}\).
\begin{definition}\label{def:linear-complex}
  Let \(P^{\bullet}\) be an object of \(\mathcal{C}_m\), described as a bigraded module
  \[P^{\bullet} = \bigoplus M_i\langle g \rangle[h]\]
  together with an internal differential \(d \colon P^{\bullet} \to P^{\bullet + 1}\).
  We say that \(P^{\bullet}\) has \defn{level \(\ell\)} for some \(\ell \in \mathbb{Z}\) if for each bigraded piece \(M_i \langle g \rangle[h]\) of \(P^{\bullet}\), we have \(g + h = \ell\).
  We say that \(P^{\bullet}\) is \defn{linear} if \(P^{\bullet}\) has level \(\ell = 0\).

>>>>

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}[theorem]{Question}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{defprop}[theorem]{Definition/Proposition}
\newtheorem{warning}[theorem]{Warning}
\crefname{notation}{Notation}{Notations}
\crefname{problem}{Problem}{Problems}

@@

Let \(P_i\) denote the indecomposable projective \(A_m\)-module defined as \(P_i = A_m\cdot e_i\).
For any integer \(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).
There is an embedding of \(A_m\text{-mod}\) into \(D^b(A_m\text{-mod})\), which sends any \(A_m\)-module as a complex of \(A_m\)-modules that is concentrated in degree \(0\).
In particular, the objects \(P_i\langle j \rangle\) can be regarded as objects of \(D^b(A_m\text{-mod})\).
\begin{definition}
  The category \(\mathcal{C}_m\) is defined to be the smallest triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\).
\end{definition}
For further discussion on the construction, see, e.g.,~\cite[Section 2.3.3]{bap.deo.lic:22}.
The category \(\mathcal{C}_m\) is \(k\)-linear and triangulated, where \([1]\) denotes the triangulated shift.
For \(X, Y \in \mathcal{C}_m\), let \(\Hom^{g,h}(X,Y)\) denote the space of morphisms in \(\mathcal{C}_m\) of internal degree \(g\) and homological degree \(h\).
In other words, we have
\[\Hom^{g,h}(X,Y) = \Hom(X,Y\langle g \rangle[h]).\]
Furthermore, for any integers \(a\) and \(b\), we have
\[\Hom^{g,h}(X\langle g' \rangle[h'], Y\langle g' \rangle[h']) = \Hom^{g,h}(X,Y).\]

@@

We now describe the full subcategory of \emph{linear complexes} of \(\mathcal{C}_m\).
It is convenient to think of an object \(P^{\bullet}\) of \(\mathcal{C}_m\)
as bigraded (projective) \(A_m\)-module equipped with a differential \(d \colon P^{\bullet} \to P^{\bullet}\).
More precisely, we can write
\[P^{\bullet} = \bigoplus_{g,h,i} M_i\langle g \rangle[h],\]
where \(g\) is the internal grading shift, and \(h\) is the homological grading shift, and 
each object \(M_i\) is a direct sum of copies of objects in \(\{P_1,\ldots, P_m\}\).
Set \(P^h\) to be the direct sum of all summands that have homological grading shift \(h\).
That is, in the notation above, we have
\[P^{h} = \bigoplus_{g,i} M_i\langle g \rangle[h].\]

\begin{warning}
  By convention, if \(M_i\) is an \(A_m\)-module, then the object \(M_i[h]\) is placed in homological degree \(-h\).
  Since the differential \(d\) raises the homological degree by one, it lowers the homological shift by one.
  That is, we have
  \[d \colon M_i\langle g \rangle[h] \to \bigoplus_{g',i'} M_{i'}\langle g' \rangle[h-1].\]
  In other words, \(d\) maps \(P^h\) to \(P^{h-1}\).
\end{warning}
\begin{definition}\label{def:linear-complex}
  Let \(P^{\bullet}\) be an object of \(\mathcal{C}_m\), described as a bigraded module
  \[P^{\bullet} = \bigoplus M_i\langle g \rangle[h]\]
  together with an internal differential \(d \colon P^{\bullet} \to P^{\bullet}\) as above.
  We say that \(P^{\bullet}\) has \defn{level \(\ell\)} for some \(\ell \in \mathbb{Z}\) if for each bigraded piece \(M_i \langle g \rangle[h]\) of \(P^{\bullet}\), we have \(g + h = \ell\).
  We say that \(P^{\bullet}\) is \defn{linear} if \(P^{\bullet}\) has level \(\ell = 0\).
